
%卒業論文用雛形
%\documentclass[a4j,12pt,oneside,openany]{jsbook}
% 英語なら以下を使う．
\documentclass[a4j,12pt,oneside,openany,english,dvipdfmx]{jsbook}

\usepackage{amsfonts,amsmath,amssymb}
\usepackage{bm}
\usepackage{float}
\usepackage[dvipdfmx]{graphicx}
\usepackage{color}
%\usepackage[dvipdfmx]{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{txfonts}
%\usepackage{ascmac, here}
\usepackage{listings}
\usepackage{color}
%\usepackage{url}
\usepackage{comment}

%jsbook を report っぽくするスタイルファイル
\usepackage{book2report}
%定理，補題，系，例題，証明などや英語用の定義がされています．
%自分なりにいじってください．
\usepackage{thesis}
% 具体的には以下のように定義されています．
% 英語の定理環境
%  \newtheorem{theorem}{Theorem}[chapter]
%  \newtheorem{lemma}{Lemma}[chapter]
%  \newtheorem{proposition}{Proposition}[chapter]
%  \newtheorem{corollary}{Corollary}[chapter]
%  \newtheorem{definition}{Definition}[chapter]
%  \newtheorem{example}{Example}[chapter]
%  \newtheorem{proof}{Proof}
% 日本語の定理環境
%  \newtheorem{theorem}{定理}[chapter]
%  \newtheorem{lemma}{補題}[chapter]
%  \newtheorem{proposition}{命題}[chapter]
%  \newtheorem{corollary}{系}[chapter]
%  \newtheorem{definition}{定義}[chapter]
%  \newtheorem{example}{例}[chapter]
%  \newtheorem{proof}{証明}
% 証明には番号をつけず，最後は Box で終わります．

\allowdisplaybreaks[1]

\newcommand{\mysps}{\ensuremath{[\![s^{\otimes}]\!]}_s}
\newcommand{\myspq}{\ensuremath{[\![s^{\otimes}]\!]}_q}
\newcommand{\myspds}{\ensuremath{[\![s^{\otimes \prime}]\!]}_s}
\newcommand{\myspdq}{\ensuremath{[\![s^{\otimes \prime}]\!]}_q}
\newcommand{\argmax}{\mathop{\rm arg~max}\limits}
\newcommand{\argmin}{\mathop{\rm arg~min}\limits}

\newtheorem{notations}{Notations}
\renewcommand{\thenotations}{\unskip}

% 英語で，見出しのフォントが気に入らなかったら
\renewcommand{\headfont}{\bfseries}

%ページ数が少ないときはここを大きくしてごまかそう！！効果絶大！！
\renewcommand{\baselinestretch}{1.1}

\begin{document}
%%%%%%%%%%%% 題目 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% ここも適当に変えてもいいと思う %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf 特 \hspace{12pt} 別 \hspace{12pt} 研 \hspace{12pt} 究 \hspace{12pt} 報 \hspace{12pt} 告}}\\
\vspace{2cm}
{\Large 題\hspace{8mm}目}\\
\vspace{1cm}
\underline{\Large{ Reinforcement Learning based Controller synthesis}} \\
\vspace{0.5cm}
\underline{\Large{ for Linear Temporal Logic Specifications }} \\
\vspace{0.5cm}
\underline{\Large{Using Limit-Deterministic Generalized B\"{u}chi Automata}} \\
\vspace{12mm}
{\large 指 導 教 員}\\
\vspace{6mm}
\underline{\Large 潮　俊光　教授}\\
　\\
%\underline{\Large Associate Professor Joe Smith}\\
\vspace{8mm}
{\large 報 告 者}\\
\vspace{6mm}
\underline{\Large 大浦　稜平}\\
\vspace{10mm}
{\Large 令和2年2月吉日}\\
\vspace{14mm}
{\Large 大阪大学基礎工学部システム科学科\\知能システム学コース}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

%%%%%%%%%%%% 概要 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  \input{thesis_abstract}
\end{abstract}


%%%%%%%%%%%% 目次 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}

%%%%%%%%%%%% 1章 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}

\input{chap1}

\begin{notations}
  For sets $A$ and $B$, $AB$ denotes their concatenation. $A^{\omega}$ denotes the infinite concatenation of the set $A$ and $A^{\ast}$ denotes the finite one. $\mathbb{N}_0$ is the set of nonnegative integers. $\mathbb{R}_{\geq 0}$ is the set of nonnegative real numbers.
\end{notations}

%%%%%%%%%%%% 2nd Chapter %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Preliminaries}

\input{chap2}

%%%%%%%%%%%% 3rd Chapter %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Reinforcement learning based control policy synthesis for LTL specifications}

\input{chap3}

%%%%%%%%%%%% 4th Chapter %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Reinforcement learning based supervisor synthesis for LTL specifications}

\input{chap4}

%%%%%%%%%%%% 5th Chapter %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusions}

\input{chap5}

%%%%%%%%%%%% Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
%%%%%%%%%%%% Appendix A %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Proofs}

\input{proof_of_lemma3_1}

\input{proof_of_thm3_1}

%%%%%%%%%%%% 謝辞 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
	I would like to express my deep sense of gratitude to my adviser Professor
	Toshimitsu Ushio, Graduate School of Engineering Science, Osaka University,
	for his invaluable, constructive advice and constant encouragement during this work.
	Professor Ushio's deep knowledge and his eye for detail have inspired me much.
\end{acknowledgement}

%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%適当に変えてねー．
\begin{thebibliography}{99}
  \bibitem{BK2008}
  C.\ Baier and J.-P.\ Katoen,
  \textit{Principles of Model Checking}.
  MIT Press, 2008.
  \bibitem{Clarke2018}
  E.\ M.\ Clarke, Jr., O.\ Grumberg, D.\ Kroening, D.\ Peled, and H.\ Veith,
  \textit{Model Checking}, 2nd Edition.
  MIT Press, 2018.
  \bibitem{KB2008}
  M.\ Kloetzer, C.\ Belta,
  ``A fully automated framework for control of linear systems from temporal logic specifications,''
  \textit{IEEE Trans.\ Autom.\ Contr.}, vol.\ 53, no.\ 1, pp.\ 287--297, 2008.
  \bibitem{Gazit2009}
  H.\ Kress-Gazit, G.\ E.\ Fainekos, and G.\ J.\ Pappas,
  ``Temporal-logic-based reactive mission and motion planning,''
  \textit{IEEE Trans.\ Robotics}, vol.\ 25, no.\ 6, pp.\ 1370--1381, 2009.
  \bibitem{WTM2012a}
  T.\ Wongpiromsarn, U.\ Topcu, and R.\ M.\ Murray,
  ``Receding horizon temporal logic planning,''
  \textit{IEEE Trans.\ Autom.\ Contr.}, vol.\ 57, no.\ 11, pp.\ 2817--2830, 2012.
  \bibitem{SU2018}
  A.\ Sakakibara and T.\ Ushio,
  ``Decentralized supervision and coordination of concurrent discrete event systems under LTL constraints,''
   in \textit{Proc.\ 14th International Workshop on Discrete Event Systems}, 2018, pp.\ 18-23.
  \bibitem{Belta2017}
  C.\ Belta, B.\ Yordanov, and E.\ A.\ Gol,
  \textit{Formal Methods for Discrete-Time Dynamical Systems}.
  Springer, 2017.
  \bibitem{Puterman}
  M.\ L.\ Puterman,
  \textit{Markov Decison Processes, Discrete Stochastic Dynamic Programming}.
  John Wiley \& Sons, Inc., 1994.

  \bibitem{WTM2012}
  E.\ M.\ Wolff, U.\ Topcu, and R.\ M.\ Murray,
  ``Robust control of uncertain Markov decision processes with temporal logic specifications,''
  in \textit{Proc.\ 51st IEEE Conference on Decision and Control}, 2012, pp.\ 3372--3379.
  \bibitem{Sadigh2014}
  D.\ Sadigh, E.\ S.\ Kim, A.\ Coogan, S.\ S.\ Sastry, and S.\ Seshia,
  ``A learning based approach to control synthesis of Markov decision processes for linear temporal logic specifications,''
  \textit{in Proc.\ 53rd IEEE Conference on Decision and Control}, pp.\ 1091-1096, 2014.
  \bibitem{Sutton}
  R.\ S.\ Sutton and A.\ G.\ Barto,
  \textit{Reinforcement Learning: An Introduction}, 2nd Edition.
  MIT Press, 2018.
  \bibitem{HU2015}
  M.\ Hiromoto and T.\ Ushio,
  ``Learning an optimal control policy for a Markov decision process under linear temporal logic specifications,''
  in \textit{Proc.\ 2015 IEEE Symposium on Adaptive Dynamic Programming and Reinforcement Learning}, 2015, pp.\ 548-555.
  \bibitem{SEJK2016}
  S.\ Sickert, J.\ Esparaza, S.\ Jaax, and J.\ K\v{r}et\`{i}nsk\'{y},
  ``Limit-deterministic B\"{u}chi automata for linear temporal logic,''
   in \textit{International Conference on Computer Aided Verification}, 2016, pp.\ 312-332.
  \bibitem{HAK2019}
  M.\ Hasanbeig, A.\ Abate, and D.\ Kroening,
  ``Logically-constrained reinforcement learning,'' \textit{arXiv:1801.08099v8}, Feb.\ 2019.
  \bibitem{Hahn2019}
  E.\ M.\ Hahn, M.\ Perez, S.\ Schewe, F.\ Somenzi, A.\ Triverdi, and D.\ Wojtczak,
  ``Omega-regular objective in model-free reinforcement learning,''
  \textit{Lecture Notes in Computer Science}, no.\ 11427, pp.\ 395--412, 2019.
  \bibitem{HKAKPL2019}
  M.\ Hasanbeig, Y.\ Kantaros, A.\ Abate, D.\ Kroening, G.\ J.\ Pappas, and I.\ Lee,
  ``Reinforcement learning for temporal logic control synthesis with probabilistic satisfaction guarantee,''
  \textit{arXiv:1909.05304v1}, 2019.
  \bibitem{BWZP2019}
  A.\ K.\ Bozkurt, Y.\ Wang, M.\ Zavlanos, and M.\ Pajic,
  ``Control synthesis from linear temporal logic specifications using model-free reinforcement learning,''
  \textit{arXiv:1909.07299}, 2019.
  \bibitem{ESS}
  R.\ Durrett,
  \textit{Essentials of Stochastic Processes}, 2nd Edition. ser. Springer texts in statistics. New York; London; Springer, 2012.
  \bibitem{ISP}
  L.\ Breuer,
  ``Introduction to Stochastic Processes'', [Online]. Available: https://www.kent.ac.uk/smsas/personal/lb209/files/sp07.pdf
  \bibitem{SM}
  S.M.\ Ross,
  \textit{Stochastic Processes}, 2nd Edition. University of California, Wiley, 1995.
  \bibitem{Singh1998}
  S. Singh, T. Jaakkola, M. L. Littman, and C. Szepes\'{v}ari,
  ``Convergence results for single-step on-policy reinforcement learning algorithms'' \textit{Machine Learning},
  vol.~38, no.~3, pp,~287--308, 1998.
  \bibitem{Owl}
  J.~Kretínsk\'{y}, T.~Meggendorfer, S.~Sickert, ``Owl: A library for $\omega$-words, automata,
  and LTL,'' in \textit{Proc.~16th International Symposium on Automated Technology for Verification and Analysis}, 2018,  pp.~543–550.
  %https://doi.org/10.1007/978-3-030-01090-4\_34
\end{thebibliography}
%\bibliographystyle{myjunsrt}
%\bibliography{refs}

\end{document}
